Wheels of Misfortune: Exploring Auto Theft Trends in Ottawa

### 2024-04-25 paper/paper.qmd
updated paper, scripts

For the data cleaning process, many variables from the original dataset was removed to focus on the necessary variables. From the original dataset, the following variables were selected: vehicle_make, vehicle_model, vehicle_year, vehicle_colour, vehicle_value, occurred_date, reported_date, weekday, recovered, year, neighborhood. For clarity purposes, the variable “year” was renamed to “theft_year” to make it clear that the variable accounted for the year the vehicle was stolen.

>>>>

For the data cleaning process, many variables from the original dataset was removed to focus on the necessary variables. From the original dataset, the following variables were selected: vehicle_make, vehicle_model, vehicle_year, recovered, year, neighborhood. For clarity purposes, the variable “year” was renamed to “theft_year” to make it clear that the variable accounted for the year the vehicle was stolen.
